---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# sfcc

The goal of sfcc is to provide fast and flexible creation of `sf` simple features geometries. 

Originally for `sfc` vectors of `POINT`, directly motivated by the set-based idioms of [silicate](https://github.com/hypertidy/silicate), and
the need to bypass the thorough checking done by the sf constructors. 

The design for the code is this: 

* c++ function for each of POINT, MULTIPOINT, POLYGON, etc. returns a list of sfg
* input is matrix of coordinates (or maybe a list) and its identifier XY (XYZ, XYZM, etc)
* groups can be specified, object, subobject, path (equivalent to gibble)
* the set-based rationale is more efficient for many cases than running the st_polygon and friends functions

For example

* `points_cpp` compiles to an internal R function
* wrap that with a `points_rcpp` R function to ensure sanity of inputs
* wrap that with a `mk_sfc_POINT` R function to organize the inputs and apply the sfc scaffolding

For MULTIPOLYGON

* `multipolygons_cpp` compiles to an internal R function
* wrap that with `multipolygons_rcpp` R function
* wrap that with `mk_sfc_MULTIPOLYGON`

What might also work is to have a single POLYGON constructor, that *optionally* applies the 
sfg level classing. Then MULTIPOLYGON wrapper can call that for each of its sub objects, with "no class please" and then apply its own class at the right level. 
But, these things are pretty simple so a bit of duplication is also ok. 


It's not finalize what the best way to specify grouping is, but it's driven from silicate. (There's hopefully a flexible set of different ways to do this, including `aes(x, y, group = ..., subobject = ...)` and other basics like earcut.hpp, silicate objects, other types). 


For now we don't consider GEOMETRY (sfc vectors with mixed topology). 


## Installation

I wouldn't use this as-is, yet. :)


## Example

This example was motivated by [this issue](https://github.com/r-spatial/sf/issues/700), trying to speed up sf creation for POINTs. 

The improvement is fairly modest, so there might be a better Rcpp way to do this? 

```{r example}
N <- 1e5
x <- data.frame(a = sample(letters, N, replace = TRUE),
                 lng = runif(N, -120, -100),
                 lat = runif(N, 30, 48))
## we avoid st_sf so we can compare apples (just the sfc creation)
sf_mk_points <- function(x, coords) {
		classdim = sf:::getClassDim(rep(0, length(coords)), length(coords), dim, "POINT")
		structure( lapply(split(as.vector(t(as.matrix(x[, coords]))),
				rep(seq_len(nrow(x)), each = length(coords))),
				## it does help to create this as a template and update in this loop
				## but not as much as list-creation in C++
				function(vec) structure(vec, class = classdim)),
			n_empty = 0L, precision = 0, crs = NA_crs_,
			bbox = structure(
				c(xmin = min(x[[coords[1]]], na.rm = TRUE),
				ymin = min(x[[coords[2]]], na.rm = TRUE),
				xmax = max(x[[coords[1]]], na.rm = TRUE),
				ymax = max(x[[coords[2]]], na.rm = TRUE)), class = "bbox"),
			class =  c("sfc_POINT", "sfc" ))
}

m <- cbind(x$lng, x$lat)
library(rbenchmark)

library(sf)
benchmark(
  sfcc_pt =  sfcc::mk_sfc_POINT(m, crs = 4326),
  sf_pt = sf_mk_points(x, coords = c("lng", "lat"))
  ,replications = 10
)




```


A polygon example (motivated by `spex::polygonize`)

```{r POLYGON}
qm <- quadmesh::quadmesh(raster::raster(volcano), z = NULL)
## a dummy structure to copy
template <- structure(list(cbind(1:5, 0)),
                      class = c("XY", "POLYGON", "sfg"))

nquads <- ncol(qm$ib)

idx <- rep(seq(0, nquads), each = 5L) + c(1L, 2L, 3L, 4L, 1L)
quadgroups <- rep(seq_len(nquads), each = 5)
idx <- rbind(qm$ib, qm$ib[1,])
xylist <- split(c(t(qm$vb[1:2, idx])), rep(quadgroups, 2L))


## slower code

system.time({
 l <- lapply(seq_along(xylist), function(ii) {
   template[[1L]][] <- xylist[[ii]]
   template
 })
})


## Rcpp code is a bit faster

library(sfcc)
## we were working with a flat vector
xylistm <- lapply(xylist, function(v) matrix(v, ncol = 2))
system.time(p <-  polygons_rcpp(xylistm))
identical(l, p)
```
